Analytical choices for analyzing multidimensional behavior - Many analysts test hypotheses about human speech.

### 2021-02-18 RR_manuscript/Draft_RR.Rmd
:art: - use pdf_document2 for now

floatsintext      : yes
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "man"
output:
  papaja::apa6_pdf:
    number_sections: true
    latex_engine: xelatex
header-includes:
  - \usepackage{cleveref}
  - \usepackage{changes}
  - \definechangesauthor[name={Stefano Coretta}, color=red]{SC}
  - \definechangesauthor[name={Timo Röttger}, color=blue]{TR}
  - \definechangesauthor[name={Joseph Casillas}, color=orange]{JC}
---

```{r setup, include = FALSE}
knitr::opts_knit$set(root.dir = here::here())
library("papaja")
r_refs("r-references.bib")
library(tidyverse)
library(patchwork)
library(brms)
library(extraDistr)
```

>>>>

floatsintext      : yes
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no
output:
  bookdown::pdf_document2:
    number_sections: true
    latex_engine: xelatex
    keep_tex: true
geometry: margin=4cm
fontsize: 12pt
header-includes:
  - \usepackage{cleveref}
  - \setlength{\marginparwidth}{2cm}
  - \usepackage{changes}
  - \definechangesauthor[name={Stefano Coretta}, color=red]{SC}
  - \definechangesauthor[name={Timo Röttger}, color=blue]{TR}
  - \definechangesauthor[name={Joseph Casillas}, color=orange]{JC}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_knit$set(root.dir = here::here())

library(tidyverse)
library(patchwork)
library(brms)
library(extraDistr)
```
